### 2017-12-10 paper/sexSelectionSpacingAppendix-ver1.tex
Removed commented out sections in Appendix
Add recall error section from paper to appendix

% \date{May 2010\\ \bigskip PRELIMINARY}
\date{October 2017}

@@

% \section{Recall Error}

@@

% \section{Why Bundle Scan and Abortion?}
% The easiest way to show why a bundled service makes sense is to model 
% the provider's problem first and then show that both provider and
% buyer will be better off if a bundled service is offered.
% Take a provider with with cost, $c_a$, of providing an abortion,
% and cost, $c_s$, of providing a scan.
% These costs include expenses for equipment, labor,
% and possibly a premium for getting caught and prosecuted. 
% The provider can either charge separately for the two services,
% in which case he will charge $p_s$ for the scan and $p_a$ for
% the abortion, or he can charge $p_b$ for the bundle.
% The provider's profit if he offers the two services separately, $\pi_{sep}$,
% to $n$ buyers, who conceive girls with the probability $p(g)$, will be
% \begin{equation}
% \pi_{sep} = n (p_s - c_s) + p(g) n (p_a - c_a).
% \end{equation}
% The first part is profit from the customers who want a scan
% and the second part is the profit from the fraction of the
% original customers who conceived a girl.
% If the provider instead offered the same $n$ buyers a bundle service
% the profit, $\pi_{bun}$, would be
% \begin{equation}
% \pi_{bun} = n p_b - n c_s - p(g) n c_a,
% \end{equation}
% since all customers pays $p_b$, all customers get a scan 
% at cost $c_s$, and the fraction $p(g)$ who conceived a girl
% would receive an abortion at cost $c_a$.
% A profit maximizing provider then picks bundled pricing if 
% $\pi_{bun} > \pi_{sep}$, or
% \begin{equation}
%  p_b > p_s + p(g) p_a.
% \end{equation}
% Assume that buyers are risk averse and that the only motivation
% for getting a prenatal sex determination test is to abort 
% female fetuses and that parents will abort the fetus if the test 
% show a female fetus (I will relax the last assumptions below).
% Furthermore, to ease exposition assume that buyers can only
% spend money on two things: consumption $c$ and prenatal sex
% determinations/abortions.
% For a buyer facing separate services the expected utility
% is then
% \begin{equation}
% U = (1-p(g)) U(c-p_s) + p(g) U(c - p_s - p_a),
% \end{equation}
% where the first part is the utility if the fetus is a boy
% and the buyers therefore only spend on the scan, which
% happens with probability $1-p(g)$, and the
% second part is the utility if the fetus is a female
% and they therefore also has to pay for the abortion,
% which happens with probability $p(g)$.
% For a buyer facing a bundled service the utility is simply
% \begin{equation}
% U = U(c-p_b).
% \end{equation}
% If follows from the standard assumptions about utility functions
% and the risk aversion assumption that
% \begin{equation}
% U(c - p_s - p(g) p_a) > (1-p(g)) U(c-p_s) + p(g) U(c - p_s - p_a).
% \end{equation}
% In other words risk averse buyers prefer a sure thing---where they pay 
% upfront---over the gamble that they either have a boy and pay only for the
% scanning or have a girl and pay for both the scan and the abortion.
% In fact, risk aversion implies that they are willing to pay 
% \emph{more} than the expected cost.
% In other words,
% \begin{equation}
% U(c - p_s - p(g) p_a - \delta) = (1 - p(g)) U(c-p_s) + p(g) U(c - p_s - p_a),
% \end{equation}
% where $\delta$ is a positive number that depends on the
% degree of risk aversion (the more risk averse the larger
% $\delta$ is).
% The provider realizes that buyers are risk averse
% and therefore offer a bundle where the price is in 
% the range
% \begin{equation}
% p_b \in [ p_s + p(g) p_a; p_s + p(g) p_a + \delta ].
% \end{equation}
% Hence, the optimal pricing scheme for both provider
% and buyer is bundled pricing, where you pay a flat fee
% and get the pre-natal sex determination and an abortion
% if needed.
% % Where the provider ends up in the possible range of
% % prices depends on the nature of the provider market.
% I implicitly assumed that the provider is risk-neutral.
% The same result hold, however, if the provider
% is risk-averse as long as there are enough potential clients.
% In that case, the law of large numbers will ensure that 
% the risk-neutral and risk-averse choices are the same
% for the provider---essentially there is no gamble if you see 
% enough clients, $p(g)$ of them will present with a female fetus 
% and $1-p(g)$ with a male fetus.
% In fact, it is possible for the provider to be \emph{more}
% risk averse than the buyers and still prefer the bundled 
% pricing scheme.
% Now imagine a situation where there there is some 
% uncertainty about whether a buyer will go through with
% the abortion after the prenatal sex determination.
% This can be represented by the probability $\rho$ that
% a buyer who had a prenatal sex determination test that
% showed a female fetus will go through with the abortion.
% If parents know that there is probability $1-\rho$ that they
% will not go through with the abortion their utility is
% \begin{equation}
% U = (1-p(g)) U(c-p_s) + p(g) U(c - p_s - \rho p_a),
% \end{equation}
% where I have made the assumption that they
% are equally happy with a boy or a girl if they
% are in the $1-\rho$ portion of the population that
% have a prenatal sex determination which show a female
% fetus but do not go through with the abortion (obviously
% this cannot be the case because if they were there
% would be no point in having the prenatal sex determination,
% but if I can show that the bundle price arise here it
% would trivially hold if there were some lower utility
% associated with having a girl than a boy).
% Because the buyers are still risk averse they would continue
% to prefer the ``sure'' thing over the gamble
% \begin{equation}
% U(c - p_s - p(g) \rho p_a) > p(b) U(c-p_s) + p(g) U(c - p_s - \rho p_a).
% \end{equation}
% The provider still offers a bundle, but the price is now 
% in  the range
% \begin{equation}
% p_b \in [ p_s + p(g) \rho p_a; p_s + p(g) \rho p_a + \delta ],
% \end{equation}
% where $\delta$ still depends on the degree of risk aversion.
% If parents on the other hand initially believe that they will always
% go through with the abortion if the fetus is female but
% still have probability $1-\rho$ that they will not, they would
% be back to the original comparison of the utility.
% \begin{equation}
% U(c - p_s - p(g) p_a) > p(b) U(c-p_s) + p(g) U(c - p_s - p_a).
% \end{equation}
% All that would do is \emph{increase} the profit for the
% provider because the law of large numbers would tell them
% exactly how many would not go through with the abortion.
% In other words, they would offer the original
% bundled price because the buyers did not know that they
% will change their mind
% \begin{equation}
% p_b \in [ p_s + p(g) p_a; p_s + p(g) p_a + \delta ],
% \end{equation}
% but the provider will have profit of
% \begin{equation}
% p_b - c_s - \rho c_a,
% \end{equation}
% which is strictly larger than the profit in either of
% the other cases.
% Also, they do not need to know which buyers are more
% or less likely to use abortion, just that some
% fraction will not use their purchased abortion.
% \clearpage
% \newpage

% \section{Simulation Results for 20 Periods}
% \begin{table}[!htp]
% \caption{Fertility and Percent Boys by Cost of \protect\linebreak Children and prenatal Sex  Determination}
% \label{tab:simul_fertility_100}
% \begin{tabular}{@{} c D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} @{}}
% \toprule
%                & \multicolumn{10}{c}{Discount rate ( $ d = 1.0 $ ) }                         \\ 
%                & \multicolumn{10}{c}{Cost of prenatal Sex Determination ($ p_s $)}                         \\ 
%                & \multicolumn{2}{c}{12} & \multicolumn{2}{c}{16} & \multicolumn{2}{c}{20} & \multicolumn{2}{c}{24} & \multicolumn{2}{c}{200} \\ \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11}
% \multirow{2}{12mm}{Cost of\\children}  & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       \\
%                                        & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} \\
% \midrule
%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
%  k = 12        &  7.46 &  50.4 &  7.46 &  50.1 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 \\
%  k = 14        &  5.40 &  52.0 &  5.40 &  50.5 &  5.40 &  50.3 &  5.41 &  50.2 &  5.43 &  50.0 \\
%  k = 16        &  4.10 &  51.5 &  4.10 &  51.5 &  4.10 &  51.4 &  4.13 &  51.1 &  4.19 &  49.9 \\
%  k = 18        &  3.13 &  54.0 &  3.13 &  54.0 &  3.13 &  54.0 &  3.14 &  53.7 &  3.25 &  50.0 \\
%  k = 20        &  2.26 &  61.0 &  2.38 &  57.9 &  2.50 &  55.1 &  2.50 &  55.1 &  2.50 &  50.0 \\
%  k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  50.0 \\
%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
%  k = 12        &  7.15 &  53.3 &  7.27 &  51.2 &  7.29 &  50.4 &  7.30 &  50.1 &  7.31 &  50.0 \\
%  k = 14        &  5.21 &  55.3 &  5.22 &  54.0 &  5.30 &  52.9 &  5.37 &  51.0 &  5.42 &  50.0 \\
%  k = 16        &  4.10 &  59.1 &  4.10 &  58.7 &  4.10 &  56.8 &  4.10 &  52.6 &  4.19 &  49.9 \\
%  k = 18        &  3.13 &  69.0 &  3.13 &  57.5 &  3.13 &  54.0 &  3.13 &  54.0 &  3.32 &  50.0 \\
%  k = 20        &  2.25 &  61.2 &  2.25 &  61.2 &  2.25 &  61.2 &  2.25 &  61.1 &  2.50 &  50.0 \\
%  k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  50.0 \\
%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
%  k = 12        &  7.07 &  61.7 &  7.10 &  57.2 &  7.14 &  54.3 &  7.24 &  52.0 &  7.34 &  50.0 \\
%  k = 14        &  5.20 &  65.2 &  5.05 &  63.3 &  5.05 &  60.6 &  5.06 &  56.3 &  5.26 &  50.0 \\
%  k = 16        &  4.06 &  75.0 &  4.06 &  71.5 &  4.06 &  63.3 &  4.06 &  60.3 &  4.16 &  49.9 \\
%  k = 18        &  3.13 &  70.0 &  3.13 &  69.9 &  3.13 &  69.7 &  3.13 &  69.0 &  3.32 &  50.0 \\
%  k = 20        &  2.98 &  70.7 &  2.81 &  68.9 &  2.25 &  61.2 &  2.25 &  61.2 &  2.63 &  50.0 \\
%  k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.25 &  49.9 \\
%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
%  k = 12        &  7.23 &  72.0 &  7.12 &  67.9 &  7.10 &  63.2 &  7.09 &  59.2 &  7.34 &  50.0 \\
%  k = 14        &  5.38 &  80.8 &  5.05 &  77.4 &  5.05 &  72.8 &  5.05 &  67.6 &  5.27 &  50.0 \\
%  k = 16        &  4.06 &  76.1 &  4.06 &  75.9 &  4.06 &  75.4 &  4.06 &  73.2 &  4.17 &  49.9 \\
%  k = 18        &  3.77 &  75.2 &  3.13 &  70.0 &  3.13 &  70.0 &  3.13 &  69.9 &  3.32 &  50.0 \\
%  k = 20        &  2.75 &  72.7 &  2.75 &  72.7 &  2.74 &  72.6 &  2.71 &  72.4 &  2.38 &  50.0 \\
%  k = 22        &  2.00 &  99.8 &  2.00 &  99.1 &  2.00 &  95.1 &  2.00 &  74.1 &  2.25 &  49.9 \\
% \begin{tablenotes} \scriptsize
% \item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 20 periods, $ I = 200 $,
%  and a probability of a son of 0.5.
% \item[a]Percent boys is the percent boys of all births.
% \normalsize
% \begin{table}[!htp]
% \caption{Fertility and Percent Boys by Cost of \protect\linebreak Children and prenatal Sex  Determination}
% \label{tab:simul_fertility_95}
% \begin{tabular}{@{} c D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} @{}}
% \toprule
%                & \multicolumn{10}{c}{Discount rate ( $ d = 0.95 $ ) }                         \\ 
%                & \multicolumn{10}{c}{Cost of prenatal Sex Determination ($ p_s $)}                         \\ 
%                & \multicolumn{2}{c}{12} & \multicolumn{2}{c}{16} & \multicolumn{2}{c}{20} & \multicolumn{2}{c}{24} & \multicolumn{2}{c}{200} \\ \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11}
% \multirow{2}{12mm}{Cost of\\children}  & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       \\
%                                        & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} \\
% \midrule
%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
%  k = 12        &  7.46 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 \\
%  k = 14        &  5.40 &  50.3 &  5.41 &  50.3 &  5.42 &  50.1 &  5.42 &  50.0 &  5.43 &  50.0 \\
%  k = 16        &  4.10 &  51.5 &  4.13 &  51.1 &  4.16 &  50.7 &  4.16 &  50.7 &  4.19 &  49.9 \\
%  k = 18        &  3.13 &  54.0 &  3.14 &  53.7 &  3.25 &  51.9 &  3.25 &  51.9 &  3.25 &  50.0 \\
%  k = 20        &  2.50 &  55.1 &  2.50 &  55.1 &  2.50 &  55.1 &  2.50 &  55.0 &  2.50 &  50.0 \\
%  k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.4 &  2.00 &  61.0 &  2.00 &  50.0 \\
%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
%  k = 12        &  7.30 &  50.8 &  7.30 &  50.3 &  7.30 &  50.0 &  7.30 &  50.0 &  7.31 &  50.0 \\
%  k = 14        &  5.24 &  53.8 &  5.40 &  51.7 &  5.40 &  50.4 &  5.40 &  50.2 &  5.42 &  50.0 \\
%  k = 16        &  4.10 &  58.9 &  4.10 &  52.6 &  4.10 &  51.5 &  4.11 &  51.3 &  4.19 &  49.9 \\
%  k = 18        &  3.13 &  54.0 &  3.13 &  54.0 &  3.13 &  54.0 &  3.13 &  53.9 &  3.32 &  50.0 \\
%  k = 20        &  2.25 &  61.2 &  2.25 &  61.2 &  2.27 &  60.8 &  2.50 &  55.1 &  2.50 &  50.0 \\
%  k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  50.0 \\
%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
%  k = 12        &  7.09 &  56.9 &  7.19 &  52.4 &  7.30 &  50.5 &  7.33 &  50.1 &  7.34 &  50.0 \\
%  k = 14        &  5.05 &  63.7 &  5.05 &  56.4 &  5.10 &  53.6 &  5.21 &  51.0 &  5.26 &  50.0 \\
%  k = 16        &  4.06 &  69.1 &  4.06 &  59.2 &  4.06 &  58.8 &  4.06 &  55.3 &  4.16 &  49.9 \\
%  k = 18        &  3.13 &  70.0 &  3.13 &  69.7 &  3.13 &  64.9 &  3.13 &  56.0 &  3.32 &  50.0 \\
%  k = 20        &  2.50 &  65.1 &  2.25 &  61.2 &  2.25 &  61.2 &  2.25 &  61.2 &  2.63 &  50.0 \\
%  k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.25 &  49.9 \\
%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
%  k = 12        &  7.07 &  67.6 &  7.08 &  60.9 &  7.13 &  54.8 &  7.26 &  51.4 &  7.34 &  50.0 \\
%  k = 14        &  5.05 &  78.3 &  5.05 &  67.8 &  5.05 &  62.7 &  5.06 &  56.7 &  5.27 &  50.0 \\
%  k = 16        &  4.06 &  76.0 &  4.06 &  75.4 &  4.06 &  69.7 &  4.06 &  63.3 &  4.17 &  49.9 \\
%  k = 18        &  3.13 &  70.1 &  3.13 &  70.0 &  3.13 &  69.9 &  3.13 &  69.7 &  3.32 &  50.0 \\
%  k = 20        &  2.75 &  72.7 &  2.74 &  72.6 &  2.64 &  71.6 &  2.00 &  62.5 &  2.38 &  50.0 \\
%  k = 22        &  2.00 &  99.1 &  2.00 &  71.8 &  2.00 &  62.5 &  2.00 &  62.5 &  2.25 &  49.9 \\
% \begin{tablenotes} \scriptsize
% \item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 20 periods, $ I = 200 $,
%  and a probability of a son of 0.5.
% \item[a]Percent boys is the percent boys of all births.
% \normalsize
% \begin{table}[!htp]
% \caption{Fertility and Percent Boys by Cost of \protect\linebreak Children and prenatal Sex  Determination}
% \label{tab:simul_fertility_90}
% \begin{tabular}{@{} c D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} @{}}
% \toprule
%                & \multicolumn{10}{c}{Discount rate ( $ d = 0.9 $ ) }                         \\ 
%                & \multicolumn{10}{c}{Cost of prenatal Sex Determination ($ p_s $)}                         \\ 
%                & \multicolumn{2}{c}{12} & \multicolumn{2}{c}{16} & \multicolumn{2}{c}{20} & \multicolumn{2}{c}{24} & \multicolumn{2}{c}{200} \\ \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11}
% \multirow{2}{12mm}{Cost of\\children}  & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       \\
%                                        & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} \\
% \midrule
%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
%  k = 12        &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 &  7.47 &  50.0 \\
%  k = 14        &  5.42 &  50.1 &  5.43 &  50.0 &  5.43 &  50.0 &  5.43 &  50.0 &  5.43 &  50.0 \\
%  k = 16        &  4.16 &  50.7 &  4.19 &  50.1 &  4.19 &  49.9 &  4.19 &  49.9 &  4.19 &  49.9 \\
%  k = 18        &  3.25 &  51.9 &  3.25 &  51.4 &  3.25 &  50.0 &  3.25 &  50.0 &  3.25 &  50.0 \\
%  k = 20        &  2.50 &  55.1 &  2.50 &  50.0 &  2.50 &  50.0 &  2.50 &  50.0 &  2.50 &  50.0 \\
%  k = 22        &  2.01 &  62.2 &  2.00 &  50.0 &  2.00 &  50.0 &  2.00 &  50.0 &  2.00 &  50.0 \\
%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
%  k = 12        &  7.30 &  50.0 &  7.31 &  50.0 &  7.31 &  50.0 &  7.31 &  50.0 &  7.31 &  50.0 \\
%  k = 14        &  5.40 &  50.3 &  5.41 &  50.1 &  5.42 &  50.0 &  5.42 &  50.0 &  5.42 &  50.0 \\
%  k = 16        &  4.10 &  51.4 &  4.16 &  50.7 &  4.19 &  50.1 &  4.19 &  49.9 &  4.19 &  49.9 \\
%  k = 18        &  3.13 &  54.0 &  3.25 &  51.9 &  3.26 &  51.9 &  3.32 &  50.0 &  3.32 &  50.0 \\
%  k = 20        &  2.50 &  55.1 &  2.50 &  55.1 &  2.50 &  55.0 &  2.50 &  50.0 &  2.50 &  50.0 \\
%  k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.24 &  55.4 &  2.00 &  50.0 &  2.00 &  50.0 \\
%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
%  k = 12        &  7.30 &  50.5 &  7.33 &  50.0 &  7.34 &  50.0 &  7.34 &  50.0 &  7.34 &  50.0 \\
%  k = 14        &  5.24 &  52.3 &  5.24 &  50.3 &  5.25 &  50.1 &  5.26 &  50.0 &  5.26 &  50.0 \\
%  k = 16        &  4.06 &  58.8 &  4.07 &  51.5 &  4.13 &  50.7 &  4.16 &  50.1 &  4.16 &  49.9 \\
%  k = 18        &  3.13 &  54.0 &  3.13 &  54.0 &  3.25 &  51.9 &  3.26 &  51.9 &  3.32 &  50.0 \\
%  k = 20        &  2.25 &  61.2 &  2.25 &  61.1 &  2.50 &  55.1 &  2.50 &  55.0 &  2.63 &  50.0 \\
%  k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.4 &  2.25 &  49.9 \\
%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
%  k = 12        &  7.12 &  53.6 &  7.31 &  50.3 &  7.33 &  50.0 &  7.34 &  50.0 &  7.34 &  50.0 \\
%  k = 14        &  5.05 &  63.2 &  5.21 &  52.6 &  5.24 &  50.3 &  5.26 &  50.0 &  5.27 &  50.0 \\
%  k = 16        &  4.06 &  61.5 &  4.06 &  59.0 &  4.07 &  51.5 &  4.13 &  50.7 &  4.17 &  49.9 \\
%  k = 18        &  3.13 &  70.0 &  3.13 &  68.3 &  3.13 &  54.0 &  3.16 &  53.5 &  3.32 &  50.0 \\
%  k = 20        &  2.43 &  69.2 &  2.00 &  62.5 &  2.00 &  62.5 &  2.25 &  55.6 &  2.38 &  50.0 \\
%  k = 22        &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.00 &  62.5 &  2.25 &  49.9 \\
% \begin{tablenotes} \scriptsize
% \item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 20 periods, $ I = 200 $,
%  and a probability of a son of 0.5.
% \item[a]Percent boys is the percent boys of all births.
% \normalsize
% \begin{table}[!htp]
% \caption{Fertility and Percent Boys by Cost of \protect\linebreak Children and prenatal Sex  Determination}
% \label{tab:simul_fertility_85}
% \begin{tabular}{@{} c D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} D{.}{.}{2.2} D{.}{.}{1.2} D{.}{.}{1.2} @{}}
% \toprule
%                & \multicolumn{10}{c}{Discount rate ( $ d = 0.85 $ ) }                         \\ 
%                & \multicolumn{10}{c}{Cost of prenatal Sex Determination ($ p_s $)}                         \\ 
%                & \multicolumn{2}{c}{12} & \multicolumn{2}{c}{16} & \multicolumn{2}{c}{20} & \multicolumn{2}{c}{24} & \multicolumn{2}{c}{200} \\ \cmidrule(lr){2-3} \cmidrule(lr){4-5} \cmidrule(lr){6-7} \cmidrule(lr){8-9} \cmidrule(lr){10-11}
% \multirow{2}{12mm}{Cost of\\children}  & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       & \mco{Avg}       & \mco{Percent}       \\
%                                        & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} & \mco{Fertility} & \mco{Boys\tnote{a}} \\
% \midrule
%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.5 $)}                         \\ 
%  k = 12        &  7.46 &  50.0 &  7.46 &  50.0 &  7.46 &  50.0 &  7.46 &  50.0 &  7.46 &  50.0 \\
%  k = 14        &  5.42 &  50.1 &  5.42 &  50.0 &  5.42 &  50.0 &  5.42 &  50.0 &  5.42 &  50.0 \\
%  k = 16        &  4.16 &  50.7 &  4.18 &  50.0 &  4.18 &  50.0 &  4.18 &  50.0 &  4.18 &  50.0 \\
%  k = 18        &  3.25 &  51.9 &  3.25 &  50.1 &  3.25 &  50.1 &  3.25 &  50.1 &  3.25 &  50.1 \\
%  k = 20        &  2.50 &  54.9 &  2.50 &  50.0 &  2.50 &  50.0 &  2.50 &  50.0 &  2.50 &  50.0 \\
%  k = 22        &  2.19 &  54.3 &  2.00 &  50.0 &  2.00 &  50.0 &  2.00 &  50.0 &  2.00 &  50.0 \\
%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.55 $)}                         \\ 
%  k = 12        &  7.30 &  50.0 &  7.30 &  50.0 &  7.30 &  50.0 &  7.30 &  50.0 &  7.30 &  50.0 \\
%  k = 14        &  5.40 &  50.2 &  5.41 &  50.0 &  5.41 &  50.0 &  5.41 &  50.0 &  5.41 &  50.0 \\
%  k = 16        &  4.15 &  50.7 &  4.16 &  50.6 &  4.18 &  50.0 &  4.18 &  50.0 &  4.18 &  50.0 \\
%  k = 18        &  3.14 &  53.8 &  3.25 &  51.9 &  3.31 &  50.1 &  3.31 &  50.1 &  3.31 &  50.1 \\
%  k = 20        &  2.50 &  55.0 &  2.50 &  54.9 &  2.50 &  52.5 &  2.50 &  50.0 &  2.50 &  50.0 \\
%  k = 22        &  2.00 &  62.4 &  2.00 &  62.1 &  2.00 &  50.0 &  2.00 &  50.0 &  2.00 &  50.0 \\
%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.6 $)}                         \\ 
%  k = 12        &  7.33 &  50.1 &  7.33 &  50.0 &  7.33 &  50.0 &  7.33 &  50.0 &  7.33 &  50.0 \\
%  k = 14        &  5.23 &  51.3 &  5.25 &  50.2 &  5.25 &  50.0 &  5.25 &  50.0 &  5.25 &  50.0 \\
%  k = 16        &  4.06 &  52.3 &  4.12 &  50.7 &  4.14 &  50.5 &  4.15 &  50.0 &  4.15 &  50.0 \\
%  k = 18        &  3.12 &  54.0 &  3.13 &  53.9 &  3.25 &  51.9 &  3.31 &  50.1 &  3.31 &  50.1 \\
%  k = 20        &  2.25 &  61.0 &  2.31 &  59.4 &  2.50 &  54.9 &  2.51 &  54.3 &  2.62 &  50.0 \\
%  k = 22        &  2.00 &  62.4 &  2.00 &  62.4 &  2.00 &  62.3 &  2.12 &  58.0 &  2.25 &  50.0 \\
%                &  \multicolumn{10}{c}{Son Preference ($\alpha = 0.65 $)}                         \\ 
%  k = 12        &  7.30 &  50.7 &  7.33 &  50.0 &  7.33 &  50.0 &  7.33 &  50.0 &  7.33 &  50.0 \\
%  k = 14        &  5.06 &  55.0 &  5.23 &  50.6 &  5.25 &  50.1 &  5.26 &  50.0 &  5.26 &  50.0 \\
%  k = 16        &  4.06 &  58.9 &  4.06 &  55.2 &  4.10 &  51.1 &  4.16 &  50.2 &  4.17 &  50.0 \\
%  k = 18        &  3.12 &  69.7 &  3.13 &  57.1 &  3.13 &  53.9 &  3.25 &  51.8 &  3.31 &  50.1 \\
%  k = 20        &  2.00 &  62.4 &  2.00 &  62.4 &  2.01 &  62.1 &  2.25 &  55.4 &  2.37 &  50.0 \\
%  k = 22        &  2.00 &  62.4 &  2.00 &  62.4 &  2.00 &  62.4 &  2.00 &  62.3 &  2.25 &  50.0 \\
% \begin{tablenotes} \scriptsize
% \item \hspace*{-0.5em} \textbf{Note.} Simulations based on  50,000 individuals, 20 periods, $ I = 200 $,
%  and a probability of a son of 0.5.
% \item[a]Percent boys is the percent boys of all births.
% \normalsize
% \begin{table}[!htp]
% \caption{Abortions and Change in Abortion Use by Cost of \protect\linebreak Children and prenatal Sex  Determination}
% \label{tab:simul_abortion_100}

>>>>

% \date{May 2010\\ \bigskip PRELIMINARY}
\date{December 2017}

@@

@@

\section{[Recall error paragraphs from paper]}

Observed sex ratios by cohort provide a straightforward way to determine 
whether recall error is a problem.
Because prenatal sex determination techniques did not become widely available until the 
mid-1980s, a higher than natural sex ratio for cohorts born before that time must be 
the result of systematic recall error.
As shown in the online Appendix, the observed sex ratio by parity becomes more male 
dominated the further back births took place.
In addition, births in the same cohort tend to be more male dominated the more recent the 
survey (births in the cohort took place longer ago relative to the survey).
Hence, there is evidence of recall error and the degree of recall error increases
with length of time between survey and cohort.

Using cohort year of birth to analyze recall error and decide which observations
to keep is, however, problematic because the year of birth for a given parity is affected 
by recall error; for example, a second born child listed as first born will be 
born later than the real first born child.
Year of marriage should, however, be unaffected by recall error.
Using year of marriage the basic recall error pattern remains with women married longer 
ago more likely to report that their child was a boy for a given parity.
Similarly, comparing women married in the same period across surveys shows
that women married longer ago are more likely to report having sons.

That recall error increases the longer ago somebody was married means
that duration of marriage is a better predictor of recall error than calendar year of 
marriage.
Figure \ref{fig:sexRatioMarriage} shows the observed sex ratio for children 
reported as first born as a function of duration of marriage combining all three surveys.%
\footnote{
The graph for second births shows a similar pattern.
The graphs for the second births and the individual survey rounds are available upon request.
}
The solid line is the sex ratio of children reported 
as first born by the number of years between the survey and marriage, 
the dashed lines indicate the 95 percent confidence interval 
and the horizontal line the natural sex ratio (approximately 0.512).
To ensure sufficient cell sizes the years are grouped in twos.

\begin{figure}[htp]%
\centering
\includegraphics[width=0.9\textwidth]{sex_ratio_marriage}
\caption{Ratio of boys in ``first'' births}
\label{fig:sexRatioMarriage}
\end{figure}

Figure \ref{fig:sexRatioMarriage} clearly illustrates the systematic recall error
problem.
The observed sex ratio is increasingly above the expected value the
longer ago the parents were married.
The increasingly unequal sex ratio with increasing marriage duration suggests that
a solution to the recall error problem is to drop women who were married ``too far'' from 
the survey year.
The main problem is establishing what the best cut-off point should be.
The observed sex ratio is consistently significantly higher than the natural sex ratio 
from around 24 years of marriage, so one possibility is simply to drop all women married 
more than 24 years at the time of the survey.
But, as the Appendix shows, there are differences across the three surveys and between 
parities.
I therefore use different cut-off points by survey round.
For NFHS-1 women married 22 years or more were dropped, with the corresponding cut-off 
points 23 years for NFHS-2  and 26 years for NFHS-3.
The final sample consists of 146,096 women, with 332,951 parity one through four births.
